---
title: "RTTWebClient"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RTTWebClient}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RTTWebClient)
library(lubridate)
```

# Example of RTTWebApi methods (basic class)

## Init Public(default) Client Obj (reference R class)
```{r}
ttWebClient <- InitPublicWebClient(server = "ttlivewebapi.fxopen.com")
#or use InitPrivateWebClient(server = "ttlivewebapi.fxopen.com", port = 8443, id = "", key = "", secret = "") to set a private connect. Need set HMAC id, key and secret
```

## Get Dividends data.table
```{r}
print(ttWebClient$GetDividendsFromWeb())
```

## Get Symbol data.table
```{r}
print(ttWebClient$GetSymbolsInfoFromWeb())
```

## Get BarHistory data.table
```{r}
print(ttWebClient$GetBarFromWeb("EURUSD", "Bid","M1", round(as.double(now("UTC")) * 1000), count = -10))
```

## Get TickHistory data.table
```{r}
print(ttWebClient$GetTicksFromWeb("EURUSD", round(as.double(now("UTC")) * 1000), count = -10))
```

# Example of RTTWebApiHost (Wrapper about RTTWebClient to make request from R easy)

## Init RTTWebApiHost obj
```{r}
ttWebApiHost <- InitRTTWebApiHost(server = "ttlivewebapi.fxopen.com")
```

## Get Dividends data.table
```{r}
print(ttWebApiHost$GetDividends())
```

## Get Symbol data.table
```{r}
print(ttWebApiHost$GetSymbolsInfo())
```

## Get BarHistory data.table
```{r}
print(ttWebApiHost$GetBarsHistory("EURUSD", "Bid","M1", now("UTC") - days(1), now("UTC")))
```

## Get TicksHistory data.table
```{r}
print(ttWebApiHost$GetTickHistory("EURUSD",  now("UTC") - days(1), now("UTC")))
```
